---
title: "Homework 5"
author: "Yan Song"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1

Read in the data.

```{r}
homicide_df = 
  read_csv("data/homicide_data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```


Let's look at this a bit

```{r}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

Can I do a prop test for a single city?

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

Try to iterate ........

```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```



```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```



```{r, error = TRUE}
city_prop_test = function(df) {
  
  n_unsovled 
  n_total 
  
  prop.test(.....)
  
}



homicide_df = 
  read_csv("data/homicide_data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL") %>% 
  nest(data = resolved)
```

# Problem 2

Start with a datafram containing all file names.
```{r}
names_df = list.files('./data')
file_names_df = str_c("./data/",names_df)
```

Iterate over file names and read in data.`

```{r include=FALSE}
output = vector("list", length = 20)
output = purrr::map(file_names_df, read_csv)

for(i in 1:20){
  output[[i]]  = mutate(output[[i]], name = names_df[[i]])
}


long_data = bind_rows(output) 

```
Here is the longitudinal dataset for the further analyses.

```{r}
 tidy_long_data = 
  long_data %>% 
  separate(name, into = c("group","id","csv")) %>% 
  select(-csv) %>% 
  select(id,group,everything()) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "observational_value"
  ) 
```

Making the spaghetti plot.

```{r}
tidy_long_data %>% 
  group_by(id,group) %>% 
  ggplot(aes(x = week, y = observational_value, group = id,color = id)) + 
  geom_line() + 
  labs(
    title = "Longitudinal Study",
    x = "time",
    y = "observations",
    caption = "Measurements by Control and Experimental Arm through Time"
  ) + 
  facet_grid(. ~ group)

```

We could see the similarity and differences between control and experimental group. First, everyone changed through 8 weeks, up and down. It is obviously that the control group generally kept in the same level through 8 weeks, however, the experimental group increased through time.


